% !TEX root = SystemTemplate.tex
\chapter{Development Environment}
The basic purpose for this section is to give a developer all of the necessary 
information to setup their development environment to run, test, and/or develop. 


\section{Development IDE and Tools}
The specific tools used to develop this project were Gedit, Vim, Putty, and g++. Except 
for g++, all of these tools are not strictly necessary to the development environment. This project 
could easily be continued in any text or code editor, with presumably, any form of Linux.  For easy construction, use the provided make file.

\section{Source  Control}
The source control used in this project was Github for both Windows and Linux. A developer could connect 
to it by several ways; the first of which is to go to the Github website, where they were included as 
contributors to the repository where the code and documentation was stored. The second was to use either 
Linux or Windows to checkout the repository and use the push and pull functions of git to keep code and 
documentation updated.

\section{Dependencies}
There are no specific dependencies with developing the system, other than a Linux operating system and gcc version three or higher.

\section{Build  Environment}
Packages are built using a general g++ command in command line Linux. A make file is also provided for easy construction.

\section{Development Machine Setup}
There are no specific steps associated with setting up a macine for use by a developer.


