% !TEX root = SystemTemplate.tex


\chapter{Project Overview}


\section{Team Members and Roles}
The team members of the Whitespace Cowboys were Kelsey Bellew, Ryan Brown, and Ryan Feather. 

\begin{itemize}
\item Kelsey Bellew was the Scrum Master.
\item Ryan Brown was the Product Owner.
\item Ryan Feather was the Technical Lead.
\end{itemize}

The team members of Lounge Against The Machine were Adam Meaney, Joseph Manke, and Alex Wulff.

\begin{itemize}
\item Adam Meaney was the Scrum Master.
\item Joseph Manke was the Product Owner.
\item Alex Wulff was the Technical Lead and Co-Scrum Master and Co-Product Owner.
\end{itemize}


\section{Project  Management Approach}
This project uses the Agile methodology. The sprints are three weeks in length, and the product backlog is hosted on Trello. Bug or trouble tickets are also to be posted on Trello, along with initial user stories. 


\section{Phase  Overview}
The initial phase that this project went through took us from conception to version 1.0.0 at which point the project changed to Lounge Against The Machine.  The current version, V2.0.0 has extended features such as a test generator and multiple test program support. It started with several planning talks and research into the technical challenges this project presented. Once decisions were made about the technical design of the system, development began.

In addition to technical challenges it took some time to clarify requirements and turn the provided user stories into the design of the current product.

Once the working version was established and most of the development in this sprint was done, the system and code were tested. A code review was done and several fixes were implemented accordingly, bringing us to a stable release of 1.0.0.  Version 2.0.0 was widely devised as a joke by Alex Wulff, but has since been modified into a respectable extension of the original.  Extensive testing on the test case generator has been completed in the attempt to provide the most detailed and customizable generator a customer could desire.


\section{Terminology and Acronyms}
See Table \ref{terms}
\begin{table}[tbh]
\begin{center}
\begin{tabular}{|r|l|}
\hline
    GNU and GNU Tools & The tools provided in most GNU\textbackslash Linux environments \\ \hline
    Agile Methodology & An approach to project management and software development \url{agilemanifesto.org} \\ \hline
    C++ Template Libraries & A built-in set of classes used for storing data. \\
    \hline
\end{tabular}
\caption{Defining Some Important Terms \label{terms}}
\end{center}
\end{table}
